\section {Appointed Positions}
\label{sec:appointed-positions}

\textbf{Board cannot force people to do these things. The descriptions should be written down and posted publicly.}
Board may appoint members to do certain tasks. Appointed officers must be voted for by at least four members of board, and should have well-defined duties. Board is highly encouraged to appoint at least the following two positions:



	\subsection{Member Liaison}

	The Member Liaison exists to bridge the gap between board and the rest of the membership. The Member Liaison is essentially a non-voting member of the board: they sit in on board meetings so they can convey to other members what board is working on and talking about, and so that they can bring up the concerns of other members to board in an organized fashion. This position cannot be held by a member of board.



	\subsection{Webmaster}

	The Webmaster is expected to update and maintain the CIF website. They should post minutes of Member and Board meetings, announcements about newly accepted members, and announcements of events, whether social or technical.
	
	The Webmaster should also update and maintain the mailing lists, under the direction of the Tech Maintenance Director and the Logistics Director.



	\subsection{External Representatives}

	To ensure consistency of representation, the Chair shall be the default representative to any external party. If necessary, the Board shall appoint floor members as additional or alternate representatives. Such appointments must be approved by a majority of Board. Representatives must report to Board after any meeting in which they represent CIF, and provide minutes if possible. Non-Board representatives cannot enter into agreements with or make commitments on CIF's behalf without prior Board approval.
