\section{Definitions}
\label{sec:definitions}

\begin{description}
  \item[CIF] CIF is defined as the shorthand name of the Computer Interest Floor and the Special Interest Housing group shall be referred to as such below.

  \item[Full Member] A Full Member is defined as any member of CIF with Full Membership rights and responsibilities as detailed below.

  \item[Associate Member] An Associate Member is defined as any member of CIF with Associate Membership rights and responsibilities but not Full Membership rights and responsibilities.

  \item[General Membership] The General Membership is defined as the entire membership of CIF, consisting of both Full and Associate Members. To be considered part of the General Membership, the individual in question must currently be registered as an Undergraduate Student at the University of Rochester.

  \item[Member] A Member is defined as any individual who is part of the General Membership.

  \item[Chair] The Chair is defined as the individual elected from the General Membership with the rights and responsibilities detailed in Section~\ref{ssub:chair} below.

  \item[Logistics Director] The Logistics Director is defined as the individual elected from the General Membership with the rights and responsibilities detailed in Section~\ref{ssub:logistics-director} below.

  \item[Tech Maintenance Director] The Tech Maintenance Director is defined as the individual elected from the General Membership with the rights and responsibilities detailed in Section~\ref{ssub:tech-maintenance-director} below.

  \item[Tech Services Director] The Tech Services Director is defined as the individual elected from the General Membership with the rights and responsibilities detailed in Section~\ref{ssub:tech-services-director} below.

  \item[Secretary-Treasurer] The Secretary-Treasurer is defined as the individual elected from the General Membership with the rights and responsibilities detailed in Section~\ref{ssub:secretary-treasurer} below.

  \item[The Board] The Board is defined as the group of five individuals currently responsible for the running, care, and maintenance, as elected by the CIF general membership at Board Elections. This group consists of the Chair, Logistics Director, Tech Maintenance Director, Tech Services Director, and the Secretary-Treasurer. Any member of the board as listed above retains all titles, rights, and responsibilities for the duration of their term.

  \item[Elected Term] An Elected Term is defined as the period in which an elected member of The Board retains all titles, rights, and responsibilities. This period consists of the time in between the beginning of the University's Spring Semester immediately after elections and the end of the University's Fall Semester following the aforementioned Spring Semester.

  \item[Appointed Position] An Appointed Position is defined as any Full Member given titles, rights, and responsibilities by The Board beyond those listed in Section~\ref{ssub:full-membership} below.

  \item[Applicant] An Applicant is defined as any student not currently part of the General Membership who is currently attending the University of Rochester and sends an application to join CIF to The Board until the time at which The Board either accepts or denies the application. Any rejected Applicant can regain Applicant status given that they once more complete the application process as detailed above.

  \item[Housing Points] Housing Points are defined as the method through which housing priority is determined amongst the General Membership. The process for assigning and determining Housing Points is detailed below.

  \item[Participation Points] Participation Points are defined as the method through which The Board determines the suitability of Full Members to retain all rights afforded to the position. The process for giving and receiving Participation Points is detailed below.

  \item[Petition] A Petition is defined as any document created by a member of the General Membership formally requesting action on the part of The Board.
\end{description}

