\section{Meetings}
\label{sec:meetings}



\subsection{Member Meetings}

Member meetings should be held at least once every two weeks, at a time to be set by The Board at the beginning of the semester.

Member meetings may be called in two ways:
\begin{enumerate}
	\item Any Board Member may call an emergency meeting for any time with any amount of advance notice --- but meetings called in this way cannot be made mandatory with less than 48 hours' advance notice
	\item One-fourth of the voting Members may sign a petition calling for a meeting to be held at any time with at least 48 hours' advance notice
\end{enumerate}

The Chair presides over Member meetings, unless they are unable, in which case the next officer in order of succession presides. Each officer is given an opportunity to report on current developments and plans within their domain.

A quorum for Member meetings is one-half of the voting Members. A quorum is required for any vote, and a proposal is approved by a Member vote if a majority of those present vote in favor of it.

If a Member is not present for three consecutive meetings without prior notification and permission of The Board, they will lose voting privileges until they have attended three consecutive meetings.



\subsection{Board Meetings}

Board meetings should be held every week, at a time to be set by the Board at the beginning of the semester.

Board meetings may be called in four ways:
\begin{enumerate}
	\item The Chair may call a Board meeting with at least 48 hours' advance notice
	\item Any two Board Members may call a Board meeting with at least 48 hours' advance notice
	\item All members of board may agree to meet at any time
	\item Logistics may arrange a Board Meeting for the purpose of interviewing potential Full Members with at least 48 hours of advance notice and quorum approval of time
\end{enumerate}

The Logistics Officer will notify the members of the times and locations of planned board meetings. A quorum for board meetings is four of the members, and is required for any board vote.

If a board meeting is called and a quorum cannot be met, the meeting must be rescheduled
