\section{Membership}
\label{sec:membership}

All Members have the following exclusive rights:

\begin{itemize}
	\item Attendance at Member Meetings (required for full members, encouraged for associates)
	\item Making Nominations for Appointed Positions
	\item Creating Petitions
\end{itemize}

In addition, all members and affiliates have the right to be notified of all events, upon the request of the individual.



	\subsection{Types of Membership}



		\subsubsection{Full Membership}\label{ssub:full-membership}

		Full Members have the following exclusive rights:

		\begin{itemize}
			\item Voting
			\item Increased Housing Points
			\item Increased priority in gaining housing through CIF
			\item Access to Members-Only Events
		\end{itemize}

		Full members have the following responsibilities:

		\begin{itemize}
			\item Payment of semesterly dues
			\item Meeting of the semesterly board-decided participation point requirement
			\item Attendance at all floor meetings
		\end{itemize}

		Full members are not required to pay dues or meet participation point requirements for their first semester as a full member.



		\subsubsection{Associate Membership}

		Associate Membership is a form of official association with CIF, intended to provide a simple way for interested parties to stay up to date with CIF activities without needing to pay dues or participate as fully as Full Members. Associate members do not have voting rights, and cannot attend member-only events. Associate Members may be only be selected to live on floor if the floor has fewer Full Members than available spaces, or at the discretion of the current Board. If living on floor, an Associate must apply for Full status by the time Membership Dues must be paid and be subject to those responsibilities.



	\subsection{Acceptance of Members}

	Anyone who wishes to become a member must apply through the membership application provided on the website. Applications are reviewed on a case-by-case basis.

	To be accepted, applicants must be interviewed at an open Board meeting. If at least four Board Members vote in favor of an applicant, they are granted a level of membership decided upon by Board. Applications for higher levels of membership may be submitted any time after their initial acceptance. Board may, with the member's approval, vote to increase membership level of the member with a vote of 4 or more without need for a reapplication.

	Off-floor Members may decrease their Membership level (from full to associate or leave entirely), provided they notify Board. Board approval is required for a change in status of an on-floor Member.



	\subsection{Floor Dues}

	At the first Board meeting of each semester, the Board must decide on both amount and deadline of dues and for that semester.

	Full Members who cannot pay their dues may request a waiver or reduction, with explanation. The waiver or reduction must be approved by a majority of Board.

	Full Members may pay their dues in the form of improvements to floor, if and only if they clear it in advance with the Secretary-Treasurer and provide receipts for all money spent.

	A Full Member who does not pay dues by the deadline set, unless they have been given a waiver or reduction, is reduced to Associate Membership.
