\documentclass[12pt]{article}
\usepackage{../common/cif}

% Creates a hyperlink to the Rochester AUP with the required label argument
\newcommand{\rochesterAUP}[1]{\href{http://www.resnet.rochester.edu/getstarted/aup.php}{#1}}

\title{CIF Acceptable Use Policy}
\date{July 12, 2014}

\begin{document}

\maketitle

\begin{abstract}
This document's purpose is to clearly define what constitutes acceptable use of the Computer Interest Floor's systems and resources. The following definitions are used throughout the entirety of this document:

\begin{itemize}
	\item ``Tech Director:'' a current CIF elected Tech Director or their designated proxy.
	\item ``Resource:'' a service, system, device, network, item, or information.
	\item ``AUP:'' an acceptable use policy.
\end{itemize}
\end{abstract}

\section{University of Rochester Acceptable Use Policy} % (fold)
\label{sec:rochester-aup}

You are not required to abide by the \rochesterAUP{University of Rochester Acceptable Use Policy} when using CIF's resources.

However, when you make use of the University of Rochester's network or resources indirectly via CIF's resources, such as when accessing the campus network or internet, the terms and conditions of the University's AUP apply \textbf{in addition to} the ones stated herein. Where conflicts exist, the University's AUP shall take precedence over CIF's. You are required to have obtained, read, understood, and consented to the \rochesterAUP{most recent copy of the University's AUP} prior to using any University of Rochester resources, directly or indirectly.

% section Rochester AUP (end)

\section{Identity Information} % (fold)

You are responsible for protecting your passwords, certificates, numeric identifiers, and other personal information. CIF's Tech Staff will do their best to ensure that such information is not compromised when within the appropriate locations of CIF systems or when in transit between those appropriate locations. If at any time you feel that your identity information is being stored in an insecure manner, or that your identity information has been or will be compromised, \techdirectorEmail{contact the Tech Director} with your complaints. Provided that you have not lodged a complaint, you are responsible for \textbf{all} activity conducted by an individual who provides your identity information. This \textbf{includes} cases where your identity information was obtained by guessing or brute force.

You may not attempt to compromise another's identity information.

% section Identity Information (end)

\section{Appropriate Access} % (fold)

If access to a resource was not intentionally granted you by the Tech Director, or you have reason to believe such access was granted, you are not permitted to access that resource. You shall not attempt to do so.

% section Appropriate Access (end)

\section{Discovery of Vulnerabilities} % (fold)

If you discover a vulnerability or unintended behavior in a CIF resource, you shall immediately \techdirectorEmail{notify the Tech Director}, without exception. You shall not attempt to exploit or ``test'' the vulnerability.

% section Discovery of Vulnerabilities (end)

\section{Profanity and Obscenity} % (fold)

You may not use CIF resources to transmit or store obscene or profane materials where doing so causes discomfort or unease in another.

% section Profanity and Obscenity (end)

\section{Legality} % (fold)

You may not use CIF resources in a way inconsistent with all applicable laws, excluding none.

You may also not use CIF resources in a way inconsistent with the \href{http://www.rochester.edu/college/odos/conduct/}{University of Rochester's rules for student conduct}. This does not include their \rochesterAUP{Acceptable Use Policy} except where \hyperref[sec:rochester-aup]{noted above}.

% section Legality (end)

\section{Malicious Use and Denial of Service} % (fold)

Because CIF's resources are shared, you may not use any resource with the intent to deny another their legitimate use of that (or any other CIF) resource, except where you have the prior explicit consent of the Tech Director.

You may also not use CIF resources in a way that causes a Denial of Service, such as consuming an unreasonably large share of system resources.

% section Malicious Use and Denial of Service (end)

\section{Entitlement} % (fold)

\begin{itemize}
	\item You are entitled to have useful, educational, and enjoyable technological resources provided you by the CIF Tech Staff as they see fit.
	\item You are \textbf{not} entitled to have access to all CIF systems and resources.
	\item Provided that you have not violated the terms of this document or otherwise engaged in conduct detractive to CIF, your access shall not be curtailed beyond that of any other individual with your affiliation with CIF.
	\item In the event that you do violate the terms of this document or another which you have read and acknowledged, your ability to access resources may be restricted or removed by the Tech Director.
\end{itemize}

% section Entitlement (end)

\end{document}
